Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-03-26 cis-perf-new-ll.tex
Updates from Overleaf

Denote the characteristics of episode $j$ as $\nu_j = (B_j, E_j, i(j))$.
I now define a series of sets $\set{E}_1, \dots, \set{E}_{N_E}, \set{E}_u$ for an integer $N_E$ such that any possible $\nu_j$ is in exactly one of the classes and each set corresponds to the possible infection episdoes that lead to identical observations (conditional on the test schedules).

If $\nu_j$ would be undetected then $\nu_j \in \set{E}_u$.
Hence, $\prob(\nu_j \in \set{E}_u \mid \vec{\theta}) = p_u$.

@@

More formally, the sets can be defined in terms of an equivalence relation $\equiv$.
Define $\equiv$ such that $\nu_j \equiv \nu_{j'}$, where $j$ and $j'$ are arbitrary possible episodes (\ie these are episodes that, a priori, could have occurred but may or may not have done), if and only if either both $j$ and $j'$ would be undetected (as defined in \cref{E-perf-test:sec:prob-undetected}) or the following four conditions all hold.
\begin{enumerate}
    \item Both $\nu_j$ and $\nu_{j'}$ would be detected.
    \item $i(j) = i(j')$.
    \item $\tau_{\sched_{i(j)}}(B_j) = \tau_{\sched_{i(j')}}(B_{j'})$.
    \item $\tau_{\sched_{i(j)}}(E_j) = \tau_{\sched_{i(j')}}(E_{j'})$.
\end{enumerate}
Then each $\set{E}_k$ is an equivalence class under this relation and the set of all possible $\nu_j$.

>>>>

Denote the characteristics of episode $j$ as $\nu_j = (B_j, E_j, i(j))$.
I now define a series of sets $\set{E}_1, \dots, \set{E}_{N_E}, \set{E}_u$ and an integer $N_E$ such that any possible $\nu_j$ is in exactly one of the classes and each set corresponds to the possible infection episdoes that lead to identical observations (conditional on the test schedules).

Define $\set{E}_u$ such that $\nu_h \in \set{E}_u$ if and only if $\nu_j$ would be undetected (if it occurred).
Hence, $\prob(\nu_j \in \set{E}_u \mid \vec{\theta}) = p_u$.

@@

More formally, the sets can be defined in terms of an equivalence relation $\equiv$ and two arbitrary possible episodes $j$ and $j'$.
Define $\nu_j \equiv \nu_{j'}$ to hold if and only if either both $j$ and $j'$ would be undetected (as defined in \cref{E-perf-test:sec:prob-undetected}) or the following four conditions all hold.
\begin{enumerate}
    \item Both $\nu_j$ and $\nu_{j'}$ would be detected.
    \item $i(j) = i(j')$.
    \item $\tau_{\sched_{i(j)}}(B_j) = \tau_{\sched_{i(j')}}(B_{j'})$, where $\tau$ is as defined in \cref{E-perf-test:eq:tau-def}.
    \item $\tau_{\sched_{i(j)}}(E_j) = \tau_{\sched_{i(j')}}(E_{j'})$.
\end{enumerate}
Then each $\set{E}_k$ is an equivalence class under this relation and the set of all possible $\nu_j$.
That is, taking any $k = 1, \dots, N_E, u$ then $\nu_j \in \set{E}_k$ and $\nu_{j'} \in \set{E}_k$ if and only if $\nu_j \equiv \nu_{j'}$.

### 2024-03-26 introduction.tex
Updates from Overleaf

\Textcite{hellewellPCRSensitivity} estimated the probability of an individual testing positive each day after infection.
This measure is highly related to the duration of positivity.
However, the study's cohort consisted only of healthcare workers, \ie working-age adults.

\Textcite{binnySensitivity} applied a slight variant of \textcite{hellewellPCRSensitivity}'s methodology to data from New Zealand.
The situation in New Zealand, who were successfully pursuing a zero-COVID strategy at this time, means that the individuals in the study were unusual.
For example, a third were travellers detected during their quarantine period on arrival to New Zealand but would have had negative RT-PCR tests before their departure.

>>>>

\Textcite{hellewellPCRSensitivity} estimated the probability of an individual testing positive each day after infection.
This measure is highly related to the duration of positivity.
However, the study's cohort consisted only of healthcare workers, \ie working-age adults, and included only 27 infections.
Therefore, the data are not suitable for inferring the full distribution in the general population.

\Textcite{binnySensitivity} applied a slight variant of \textcite{hellewellPCRSensitivity}'s methodology to data from New Zealand.
The situation in New Zealand, who were successfully pursuing a zero-COVID strategy at this time, means that the individuals in the study were unusual.
For example, a third were travellers detected during their quarantine period on arrival to New Zealand but would have had negative RT-PCR tests before their departure.
Furthermore, asymptomatic infections were excluded due to limitations of their methodology.
Duration of positivity may be correlated with severity of symptoms, and hence this exclusion could bias their results.
